European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-06 manuscript/manuscript.qmd
Add pro-Africa references

First, European powers may favour geographically proximate borrowers — in other words, a continental preference — leading to disproportionately favourable treatment of European recipients. Second, given the historical legacy of colonialism, particularly in Africa, European powers might be more inclined to support former colonies (colonial preference), especially those with enduring political, economic, or cultural ties.

>>>>

First, European powers may favour geographically proximate borrowers — in other words, a continental preference — leading to disproportionately favourable treatment of European recipients. Second, given the historical legacy of colonialism, particularly in Africa, European powers might be more inclined to support former colonies (colonial preference), especially those with enduring political, economic, or cultural ties [@moyo2024; @stone2004; @stone2011, p.51].
